\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper, margin=1.0in}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{comment}
\usepackage[dvipsnames]{xcolor}
\usepackage[backend=biber]{biblatex}
\addbibresource{dust_halos.bib}

%SetFonts

%SetFonts


\title{Circumgalactic dust halos update \#2}
\author{Jacqueline McCleary}
%\date{}							% Activate to display a given date or no date

\newcommand{\dMdp}{\rm \frac{\partial M}{\partial \rho}} 
\newcommand{\dMinline}{$\rm \partial M / \partial \rho$~}
\newcommand{\av}{$A_V$~}

\begin{document}
\maketitle

\section{Executive Summary}

\begin{enumerate}
	\item Literature review -- very recent developments in modeling
	\item Accompanying modeling updates (and code improvements)
	\item Updated results based on new models -- including fitting power laws! The TL;DR is that while the \textit{slope} for all redMaGiC-based XXX samples XXX is a very close match to the M\'{e}nard result, the \textit{amplitude} is about twice as high. This is something we can and should look into in future work.  
	\item For the first time, I have also expand our search for extended dust halos to the Northern Sky! I tried a few different SDSS background samples as well as two different foreground samples: WISExSCOS and GWSLC (itself divided by specific star formation rate). foreground samples. While the WISExSCOS x SDSS results tended to be consistent with the redMaGiC samples at \textit{low} impact parameters, at \textit{high} impact parameters ($>$ XX arcminutes), the extinction flattens out and doesn't decrease. Meanwhile, the GWSLC x SDSS extinction has an interesting dip at intermediate impact parameters but agrees with the redMaGiC curves at high and low impact parameters. 
	\item Also, my talk at the Aspen Center for Physics dust workshop went really well! There were good questions and a lot of interest afterwards. 
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%
%%%%%%% LITERATURE REVIEW
%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Literature Review}\label{sec:literature}
Since I prepared my last update, several exciting and highly germane papers have been published. Results include an interesting hydrosim study of dust survival in the IGM, a new model for dust extinction, and an update to the canonical SFD map. 
\subsection{Gordon et al. 2023}
described in \cite{2023ApJ...950...86G}. Implemented with the \texttt{dust\_extinction} software package \cite{Gordon2024}. 
\subsection{Helena outflow paper}
\subsection{CSFD}
\subsection{Dust as a supernova systematic}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%
%%%%%%% CODE AND MODEL UPDATES
%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%
%
\section{Code and Modeling Updates}\label{sec:code}


%%%%
%%%% COLOR-MATCHED RANDOMS
%%%%

\subsection{Code updates}
\subsubsection{Color-matched randoms}
\begin{itemize}
	\item describe algorithm, show nice figure
	\item This didn't significantly affect the result, however.
\end{itemize}

%%%%
%%%% RANDOM CATALOG GENERATION OVERHAUL
%%%%
\subsubsection{Random catalog generation overhaul}
\begin{itemize}
	\item Mention bug of picking healpixels; could even show the bad ra/good ra figures
	\item Also implemented ability to generate catalogs in galactic coordinates, which made sense for the WISExSCOS catalog
	\item Based on the redMaGiC ratio of random galaxies to real galaxies, the random catalogs I create are $\sim 20 \times$ the length of their respective data catalogs. For very large galaxy catalogs like SDSS, generating an equivalent random catalog with almost a billion objects is too much for my HPC to handle. (Or, perhaps my code is inefficient.) So, I added a little option to create multiple smaller catalogs and concatenated them. % I feel like this doesn't actually need to be said. 
\end{itemize}

%%%%
%%%% RANDOM CATALOG GENERATION OVERHAUL
%%%%
\subsubsection{Treecorr variance and misc. utilities}
\begin{itemize}
	\item Fixed variance! Used patches and compensated estimates
	\item \texttt{RADec\_to\_healpixel}
	\item deredden magnitudes, the script used to incorporate CSFD extinction values into magnitudes.
	\item fix magnitude (idnr what that is) 
\end{itemize}

%%%%
%%%% 
%%%%
\subsection{Model improvements}

\subsubsection{Gordon 2023 extinction}
\begin{itemize}
	\item At the workshop, Daniella Calzetti told me that she was flattered but that I needed to update the extinction law that I was using. She pointed me to the Gordon 2023 paper referenced above.
	\item I found the \texttt{dust\_extinction} repository\footnote{\url{https://github.com/karllark/dust_extinction}} and used that.
	\item It did shift our values, but the changes are irrelevant since the previous values were so out of date!
\end{itemize}

\subsubsection{CSFD}
\begin{itemize}
\item As metioned earlier, Nao pointed me to this CSFD paper, where the amplitude of the residual seemed non-negligible ($10^4$) and so worth implementing. 
\item I located a nice software package called \texttt{dustmapper}\footnote{\url{https://github.com/gregreen/dustmaps}} to query the CSFD dust map and obtain extinction coefficients for a given set of coordinates. Specifically, there is a handy \texttt{dustmaps.csfd.CSFDQuery} method that takes as input an RA, Dec list in SkyCoords format and returns an array of E(B-V) values. An $R_V$ value is used to convert those into extinction coefficients and then used to de-redden SDSS and DES magnitudes. Using SFD maps to obtain E(B-V) 
Applying band-specific extinction coefficients to get extinction values.
\item Subtracting these extinction values A$_{\rm X, CSFD}$ from the observed magnitudes \texttt{MAG\_X} to obtain the dereddened magnitudes:
\begin{verbatim}
MAG_X_CORRECTED = MAG_X - A_X_CSFD
\end{verbatim}

For the DES magnitudes, I used the corrected magnitude prescription of Pandey et al.~2021: 
\begin{verbatim}
MAG_CORRECTED = MAG + DELTA_MAG_Y4 + DELTA_MAG_CHROM - A_X_CSFD
\end{verbatim}
\item As one might expect, this had a notable effect on the amplitude of the signal. 
\end{itemize}


\begin{comment}
% Dereddening workflow 
Load up some coordinates in SkyCoords format
Get E(B-V) for those galaxies with dustmap package.
Multiply that  E(B-V) value by RV to get an AV: 0.302*3.1 = 0.9331  
Use dust_extinction to get the A(X)/A(V) extinction curve as I have always done…
Multiply extinction curve A(X)/A(V) by the AV I calculated to get AX
Subtract the AX from magnitudes to get de-reddened magnitudes!
\end{comment}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%
%%%%%%% CATALOGS
%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Catalogs: Round 2}\label{sec:catalogs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%
%%%%%%% RESULTS
%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Results}\label{sec:results}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%
%%%%%%% DISCUSSION
%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Discussion and Next Steps}\label{sec:discussion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%
%%%%%%% BIBLIOGRAPHY
%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\printbibliography

\end{document}  