\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

%SetFonts

%SetFonts


\title{Useful words and turns of phrase for paper}
\author{Jacqueline McCleary}
%\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle
%\section{}
%\subsection{}

From my CAREER
The circumgalactic distribution of dust will be influenced by complex processes including feedback-driven galactic winds, cooling flows, ram pressure stripping of orbiting satellites, and accretion from the surrounding large-scale structure. Thus, it could be expected that the properties of circumgalactic cool gas and dust will vary depending on intrinsic and environmental properties of the central galaxy. If this is the case, results from observational studies of the cool CGM could be biased by properties of the foreground galaxy sample.
\noindent
While the details of its interaction with electromagnetic radiation will depend on the physical characteristics of the grain in question, 
%(morphology, refractive index, size, etc.~), 
dust is an efficient absorber of UV-optical light. %and radiates in submillimeter wavelengths.  


From Menard 2010: 

``Our observational results primarily make use of the angular cross-correlation between the brightness of quasars and the projected density of galaxies'' 

``Secondly, this large sample – together with high accuracy photometry in five optical pass bands – allows us to detect the presence of dust in the intervening space and explore its distribution and properties. This allows us to study the properties of intergalactic dust, and provides a way of inferring the abundance of dust in the Universe.''

``On small scales ($<0.01$), the signal contributions from magnification and dust extinction are expected to be dominated by Poisson noise. For larger scales, measurements from different angular bins become significantly correlated, as one would expect since different quasars sample the same local population of galaxies.'' \textbf{What to do about this isn't clear}. I *still* think this is what's behind the fat tail, though I feel like I tested this before and never got a satisfactory answer. Oh right, the Y1 mask was effectively a test of this. It might be worth trying again... or I could just leave it alone. 

From ARA\&A Cosmic Metals paper:

``Although their mass grows with time, only a minority of the baryonic matter is found in stars; even today, some 13.7 Gyr after the Big Bang, $>90\%$ 
of the baryons are found in the gaseous phase of the Universe. The gas, notably the cold gas traced by HI and H$_2$, provides the reservoir of fuel for forming stars.''

From Helena Richie dust outflow paper (her introduction is just generally gold)

``The presence of dust in the interstellar medium (ISM) can enhance the star formation rates in galaxies because dust serves as a cooling channel for gas (Whitworth et al. 1998), a catalyzing surface for the formation of molecular hydrogen (Hollenbach \& Salpeter 1971), and a shield from molecular photodissociation by ultraviolet starlight (Draine \& Bertoldi 1996)—all of which aid in galaxies’ abilities to form stars. However, dust grains have also been observed to hold a significant portion of the ISM’s metal content (Dwek 1998; Weingartner \& Draine 2001) and have the potential to accrete metals from the gas phase (Dwek 1998; Hirashita 1999; Jenkins 2009), which could decrease the efficiency of gas cooling. Thus, an understanding of cosmic dust evolution in galaxies is critical to an overall theory of galaxy evolution.''

``A growing number of observations show that extragalactic dust is abundant in the Universe (Zaritsky 1994; Chelouche et al. 2007; Ménard et al. 2010; McGee \& Balogh 2010; Ménard \& Fukugita 2012; Hodges-Kluck \& Bregman 2014; Peeples et al. 2014; Peek et al. 2015; Smith et al. 2016). For example, using reddening in observations of gravitationally lensed quasars in galaxy halos, Ménard et al. (2010) found that extragalactic dust accounts for roughly half of the cosmic dust mass and can extend out to megaparsec scales. However, the source of such vast amounts of extragalactic dust is unclear given that dust is thought to form predominantly in the ISM through condensation in stellar winds and supernovae (Dwek & Scalo 1980; Gehrz 1989; Moseley et al. 1989).''

``It is also unclear how the morphological properties of dust grains may be altered through these processes. In the ISM, dust grains range in diameter from nanometers to microns (Wein- gartner & Draine 2001). Their sizes can also change with time— dust can grow through coagulation (Asano et al. 2013; Hirashita & Chen 2023) and shrink due to shattering (Jones et al. 1996; Asano et al. 2013). It can also be destroyed altogether due to sputtering (Draine & Salpeter 1979). The efficiency of these mechanisms in outflows is unknown. In particular, observations suggest that the abundance of small grains in the circumgalactic medium (CGM) is comparable to that of the ISM (Wolfire et al. 1995). At first glance, this is puzzling, since theoretical models predict that the virial temperatures of massive galaxies should be hot enough to destroy small grains (Spitzer 1956; Strickland et al. 2004; Anderson & Bregman 2010). It is unclear whether the source of extragalactic dust directly supplies small grains to the CGM or if they are formed in situ through shattering (Jones et al. 1996).''

From Bryanne:
 ``Circumgalactic dust halos of foreground galaxies can cause excess reddening, biasing photometric redshift estimates and therefore estimates of cosmological parameters.'' There is actually a Hirata paper on this, which I should consult again. 
\end{document}

pecifically, they use the Cholla code to set up ``wind tunnel'' simulations of cool, dusty clouds driven into the hot halo by star formation activity. They find that that 60\% of 0.1-micron sized dust grains entrained in these galactic outflows could survive to populate both the hot and cool phases of the halo. Meanwhile, grains smaller than 0.01 microns cannot withstand hot-phase exposure and must be created in situ. Another good reference is R.~Kannan et al.~2021 \cite{2021MNRAS.503..336K}, which examines dust entrainment in galactic winds using hydrodynamic simulations

``Survey masks are essential for constructing catalogs matched to one another in sky coverage. Failure to properly implement proper masking for both real and random catalogs may artificially boost or suppress correlation signal.'' 
% This is the robot speaking, need ti make it my own. 
%``The correlation function effectively measures the clustering relative to a random field. If the "random" field does not have the same exclusion zones, then where the data has zeros (in the masked areas), the random field has non-zero values.'' 

Introduction

From CGM review
``If a great majority of baryons are not locked in stars within galaxies, where are they? The first possible answer is that most baryons have never been incorporated into galaxy halos to begin with, and they remain in the IGM. While observations of the Lyman-alpha (Lyα) forest indicate that this is the case at high redshifts (z > 2, e.g., Rauch, 1998), the cool IGM’s share of the cosmic baryon budget appears to be a factor of several times lower in the present day. Another possibility is that a large fraction of baryons were once accreted into dark matter halos, but they had since been heated and possibly expelled out of halos due to energetic feedback processes from galaxies, and they now reside in a warm-hot ionized phase (WHIM; e.g., Bregman, 2007; McQuinn, 2016). However, detecting WHIM is extremely challenging due to the expected low densities and high temperatures (T ∼ 105−7 K; nH < 10−4 cm−3), and empirical constraints on their baryonic content remain highly uncertain to date. The final scenario is that baryons reside within dark matter halos, but unlike ISM gas they are too diffuse and therefore difficult to detect in emission. Characterizing the physical properties of the CGM and accounting for its various gas phases and how they relate to the baryon budget is therefore of great importance to solving this problem and distinguishing between the three scenarios above.''

For SNe in particular, Ménard et al. (2010b) show that dust affects cosmological parameters such as the matter density of the universe $\Omega_m$ and the dark energy equation of state parameter $w$ at the level of a few per cent, which is comparable to the current statistical errors. 


For discussion:
`` Despite being an ensemble average over many galaxies, these spatial profiles serve as a baseline characterization for the changing ionization condition and chemical enrichment in the galactic atmosphere. Investigating how these profiles vary with the galaxy mass, star formation history, and environments provides key insights into the origin and primary drivers that dictate the physical state of the gas.''

``The contributions from the one-halo term are all given by the
mass elements inside of the host halo. Specifically, ∆Σ1h(R) is
given by the three components: (1) the stellar mass density of the
central galaxy, ∆Σ∗(R), (2) the dark matter density of the central
halo, ∆Σcen(R), and (3) the mass density of the satellite galaxies,
∆Σsat(R). The two-halo term arises from the matter of the satellite galaxies in neighbouring halos that are correlated with the large-scale
distribution of dark matter in the host halos (Yang et al. 2006).
As the scale increases, the two-halo term is supposed to gradually dominate the ESD signals. 
Acknowledgements

This research makes use of the SciServer science platform (www.sciserver.org). 
SciServer is a collaborative research environment for large-scale data-driven science. It is being developed at, and administered by, the Institute for Data Intensive Engineering and Science at Johns Hopkins University. SciServer is funded by the National Science Foundation through the Data Infrastructure Building Blocks (DIBBs) program and others, as well as by the Alfred P. Sloan Foundation and the Gordon and Betty Moore Foundation.